\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

\emph{To make space more accessible, launch costs must be reduced. Consequently, companies are moving towards reusable launch vehicles. Consider, for example, how impractical it would be to scrap an aircraft after every flight—flying would become prohibitively expensive. However, research into applying reinforcement learning to address this issue remains limited, hence the motivation for this thesis.
}

\emph{On a personal note, this Thesis allowed me to cap off 5 years of studying at TU Delft. I decided on Aerospace Engineering during high school due to a curiosity about rockets and space exploration. Through my bachelors I developed interests in machine learning and particularly reinforcement learning. Following this, my interests in controls spiked during a year as a controls engineer at Forze. Rockets, controls and reinforcement learning are the main pillars of this thesis; and I think I am very privileged to have worked on a project for 9 months of which I like the topics so much.
}

\emph{I would like to thank my supervisor Dr. ir. Erik-Jan van Kampen for his support and advice, without which I would have been lost. Secondly, I extend my thanks to all the lecturers who have taught me.}

\emph{During this thesis I realised that most essential knowledge is acquired in the first 2 years of the bachelors. So simply put, my advice to all students wishing to pursue becoming aerospace engineers is: attend your lectures.
}

\begin{flushright}
{\makeatletter\itshape
    \@author \\
    Delft, \monthname{} \the\year{}
\makeatother}
\end{flushright}